Think deep for reef resilience

### 2025-09-25 paper/paper_draft.qmd
Reduce unnecessary repetition

![Time series of coral cover (relative to reef area) categorised within each Management area
(rows), for each GCM analysed (columns) based on temporal behaviour over 2030 and 2060. The
time series are categorised as "Low" (green), "Medium" (in orange), and "High" median cover
(in blue). Solid lines represent the cluster median time series and bands represent the 95th
percentile confidence
intervals.](../figs/GCM_cover_timeseries_plot.png){#fig-gcm-cover-trajectories
fig-align="center" width="14.82cm"}

@@

![Median depth for reefs within each bioregion, separated into clusters assigned by time
series clustering. ‘Low’ clusters (green) are clusters with the lowest median area-relative
cover between 2030 and 2060 within each bioregion. ‘Medium’ clusters (orange) are clusters
with intermediate median area-relative cover between 2030 and 2060 within each bioregion.
‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030
and 2060 within each bioregion. Solid lines represent the median depth for each cluster
across reefs and bands represent the distribution of depth values within each cluster.
Displays results for ACCESS-ESM1-5
GCM.](../figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth
fig-align="center" width="14.82cm"}

>>>>

![Time series of coral cover (relative to reef area) categorised within each Management area
(rows), for each GCM analysed (columns) based on temporal behaviour over 2030 and 2060. The
time series were clustered into "Low" (green), "Medium" (orange), and "High" (blue) clusters
indicating their relative median coral cover. Solid lines represent the cluster median time
series and bands represent the 95th percentile confidence
intervals.](../figs/GCM_cover_timeseries_plot.png){#fig-gcm-cover-trajectories
fig-align="center" width="14.82cm"}

@@

![Median depth for reefs within each bioregion under ACCESS-ESM1-5, separated into clusters
assigned by time series clustering. Time series were clustered based on their behaviour
between 2030 and 2060. Time series with comparatively low median area-relative cover is
indicated in green, intermediate cover in orange, and high in blue. Solid lines represent
the median depth for each cluster across reefs and bands represent the distribution of depth
values within each
cluster.](../figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth
fig-align="center" width="14.82cm"}
